Stability concerns in random matrices

### 2018-03-17 random_matrix_stability.Rmd
Add introductory paragraph

@@

```{r, echo = TRUE, eval = TRUE}
mag_var <- read.table(file = "var_gen_mag.csv", header = TRUE, sep = ",");
stabi_3 <- mag_var[,3] / 1000000;
par(mar = c(5, 5, 2, 1));
plot(x = log10(mag_var[,1]), y = stabi_3, type = "b", lwd = 2, ylim = c(0, 0.0005),
     xlab = "LOG Generation time variation among species", ylab = "Proportion stable",
     cex.axis = 1.5, cex.lab = 1.5, lty = "solid");
```

>>>>

********************************************************************************

**Analyses of dynamic systems using random matrices find that stability generally decreases with increasing system size. But in ecological communities, the magnitude of interaction effects will be highly dependent upon species generation time. The per capita effect of individuals from species with relatively short generation times will be lower than that of individuals from species with longer generation times. Interaction effects on are therefore expected to be non-random within species, with some species having consistently weaker or stronger effects on other species per capita. Here we show that by accounting for variation in generation time among species across three orders of magnitude, community stability is substantially increased. Further, the influence of variation in generation time becomes exponentially more important as community size increases. We suggest that variation in species generation time might be a key contributor to stability of large ecological communities.**

********************************************************************************

The above is a draft introductory paragraph or abstract. I believe that we could get [an article on the above](https://www.nature.com/natecolevol/about/content) clearly in the space of 3500, or maybe even 1500 words. As far as I've been able to find, such an article would be novel and interesting (and mathematically correct).

@@

```{r, echo = TRUE, eval = TRUE}
mag_var <- read.table(file = "var_gen_mag.csv", header = TRUE, sep = ",");
stabi_3 <- mag_var[,3] / 10000000;
par(mar = c(5, 5, 2, 1));
plot(x = log10(mag_var[,1]), y = stabi_3, type = "b", lwd = 2, ylim = c(0, 0.0005),
     xlab = "LOG Generation time variation among species", ylab = "Proportion stable",
     cex.axis = 1.5, cex.lab = 1.5, lty = "solid");
```
